---
title: "NCRN Bird QC"
output: html_document
knit: (function(inputFile, encoding) { 
          rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file='NCRN_Bird_QC.html') })

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(NCRNbirds)
library(tidyverse)
library(DT)
library(lubridate)

options(htmlwidgets.TOJSON_ARGS = list(na = 'string'))

NiceTable<-function(DF){
   

   datatable(DF, rownames = F, extensions = "Buttons", autoHideNavigation = T, options=list(
      columnDefs=list(list(className='dt-center', targets=0:ncol(DF)-1 )),
      pageLength=25,
      dom='Btip',
      buttons=c('copy','csv'))
   )}

errorText<-function(text) {cat(paste0("<span style='color:red;'>",text,"</span><br>"))}

DataDir<-"C:/Data/Birds_NCRN/"

NCRN<-importNCRNbirds(DataDir)

QCYears<-c(2007:2019)

QCPoints<-getPoints(NCRN, years = QCYears)

QCVisits<-getVisits(NCRN, years = QCYears)

QCBirds<-getBirds(NCRN, years=QCYears, flyover=T,incidental = T, juvenile = T) 

```



```{css, echo=FALSE}
h1, h2, h3 {
  text-align: center;
}

.nav>li>a {
   padding: 10px;
}
```

#  {.tabset .tabset-pills .tabset-fade}

## Introduction

**Run on:** `r format(Sys.Date(),"%B %d %Y") `.

**Years covered:** `r paste0(min(QCYears),"-", max(QCYears)) `.


### The following data is not currently QCed:

#### Points
- The following are not exported:
   + Unit Group 
   + Sub Unit Code
   + UTM Zone and Coordinates
   + Datum
   + Levels 3 and 4 Omernik Names
   + BCR 
   + Location type

#### Visits
- Need to verify reasonable min, max and daily ranges for temperature and humidity. 
- Contact_Role is currently all NA - no need to export that
- We need a list of Observers and years to compare to the data.


#### Birds
- Need to create a master list of all AOU codes, Latin and common names, taxon codes and TSNs that we accept as valid
- Formatting of text in interval lengths is inconsistent (space around dashes or not)
- ID method codes are sometimes capitalized and sometimes not and have mystery number codes and should be cleaned up.
- Sex ID code 0 and 1 seem to be interchangeable. What is going on there? Has this evolved over time?
- Need to export the Previously_Obs (previously observed) data.
- Need to decide if there is any way to ferret out suspicious bird counts. 


## Points

```{r Point-QC, child="01_BirdPointsQC.Rmd"}
```

## Visits

```{r Event-QC, child="02_BirdVisitsQC.Rmd"}
```

## Bird Data

```{r FieldData-QC, child="03_FieldDataQC.Rmd"}
```



